# tbl_hierarchicial()

## Adverse Event Reporting (and friends)

Use `tbl_hierarchicial()` and `tbl_hierarchicial_count()` for reporting of AEs, Con Meds, and more.

```{r}
#| label: create-ae-tbl
tbl_ae <- adae |> 
  tbl_hierarchical(
    by = "ARM2", 
    variables = c("AESOC", "AEDECOD"),
    id = "USUBJID",
    denominator = adsl
  )
```

```{r}
#| echo: false
#| label: print-ae-tbl
tbl_ae
```

## ARD + QC

ARDs are **wonderful** for QCing {gtsummary} tables. 😻

- The ARD include the formatted and un-formatted numbers that appear in the table.

- Extract the ARD from the {gtsummary} table.

- Build fresh ARD from source data, and compare it to the ARD from the table.

## ARD + QC: Extract ARD

```{r}
#| eval: false
gather_ard(tbl_ae)
```

```{r}
#| label: gather-ae-tbl-ard
#| echo: false
#| message: true
gather_ard(tbl_ae)[[1]] |> 
  dplyr::filter(variable == "AEDECOD")
```


## ARD + QC: Build and Compare ARDs

```{r}
#| label: build-ae-tbl-ard
ard_ae <- adae |> 
  cards::ard_stack_hierarchical(
    by = "ARM2", 
    variables = c("AESOC", "AEDECOD"),
    id = "USUBJID",
    denominator = adsl
  )
```

The next step is to simply compare the two ARDs to confirm results.
As this is done programmatically, it is quick to repeat as data continues to accrue.

::: {.small}

There are numerous ways to compare objects in R.
We are currently developing a tool in {cards} that will streamline ARD comparison, with sensible defaults for ARDs.
Stay tuned! 📺
:::

